%-------------------------
% Resume in Latex
% Author : Vaishanth
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}%\setmainfont{Times New Roman}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\RequirePackage{tikz}
\RequirePackage{xcolor}

\definecolor{cvblue}{HTML}{0E5484}
\definecolor{black}{HTML}{130810}
\definecolor{darkcolor}{HTML}{0F4539}
\definecolor{cvgreen}{HTML}{3BD80D}
\definecolor{taggreen}{HTML}{00E278}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{name}{black}
\colorlet{tagline}{darkcolor}
\colorlet{heading}{darkcolor}
\colorlet{headingrule}{cvblue}
\colorlet{accent}{darkcolor}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% \usepackage[T1]{fontenc}
% \usepackage[T1]{fontenc}
% \usepackage{cochineal}
% \usepackage{fourier}

% \usepackage{fontspec}
% \usepackage{polyglossia}
% \setmainlanguage{german}
% \setmainfont{Times New Roman}

% serif
\usepackage{CormorantGaramond}
\usepackage{charter}

% \pagestyle{fancy}
% \fancyhf{}  % clear all header and footer fields
% \fancyfoot{}
% \renewcommand{\headrulewidth}{0pt}
% \renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}
\urlstyle{same}

\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & \textbf{\small #2} \\
      \textit{\large#3} & \textit{\small #4} \\
      
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSingleSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & \textbf{\small #2} \\
      
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.1in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand\sbullet[1][.5]{\mathbin{\vcenter{\hbox{\scalebox{#1}{$\bullet$}}}}}

%-------------------------------------------\usepackage{fontspec}
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
%----------HEADING----------


\begin{center}
    {\huge Kong Ji Yu} \\ \vspace{2pt} 
    {+60 10-2407930} ~ 
    \small{-}
    \href{https://www.overleaf.com/read/pknmtygnwbzx#9ef4bb}{\color{blue}{Portfolio}} ~ 
    \small{-}
    \href{mailto:kongjiyu0198@gmail.com}{\color{blue}{kongjiyu0198@gmail.com}} ~ 
    \small{-}
    \href{https://www.linkedin.com/in/ji-yu-kong-249516279/}{ \color{blue}{linkedin.com/in/kongjiyu}}  ~
    \small{-}
    \href{https://github.com/kongjiyu}{ \color{blue}{github.com/kongjiyu}} ~
    \vspace{-7pt}
\end{center}

%-----------EDUCATION-----------
\section{\color{airforceblue}EDUCATION}
  \resumeSubHeadingListStart
  \resumeSubheading
      {Tunku Abdul Rahman University of Management and Technology (TAR UMT)}{}
      {Bachelor of Software Engineering with Honours}{June 2025 - Present}
    

    \vspace{-4pt}
     \resumeSubheading
      {Tunku Abdul Rahman University of Management and Technology (TAR UMT)
}{}
      {Diploma in Computer Science}{June 2023 - May 2025}
        \resumeItemListStart
    \resumeItem{CGPA: 3.9 / 4.0}
  \resumeItemListEnd
  \resumeSubHeadingListEnd
  \vspace{-10pt}

%-----------PROGRAMMING SKILLS-----------
\section{\color{airforceblue}TECHNICAL SKILLS}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{\normalsize{Programming Languages:}}{ \normalsize{Javascript, React, Java, Assembly, MySQL, Shell Script, Python}} \\
      \vspace{1.2pt}
      
     \textbf{\normalsize{Libraries and Tools:}}{ \normalsize{Git, Docker, datatables, FlyonUI, MagicUI}} \\
      \vspace{1.2pt}
      
     \textbf{\normalsize{Cloud:}}{ \normalsize{Oracle Cloud Infrastructure, Firebase}} \\
     \vspace{1.2pt}

     \textbf{\normalsize{Languages:}}{ \normalsize{Chinese, English, Malay}}

     % copy and paste above textbf block to add more 
     }}
 \end{itemize}
 \vspace{-16pt}
 
 %-----------EXPERIENCE-----------
\section{\color{airforceblue}WORK EXPERIENCE}
  \resumeSubHeadingListStart

    \resumeSubheading
      {CRM \& Cloud Intern}{} 
      {Global Genesis, Malaysia}{September 2024 - January 2025}
      \resumeItemListStart
        \resumeItem{Configured Oracle Cloud Compute infrastructure and supported initial deployment for CRM-related services.}
        \resumeItem{Led CRM data migration and database configuration tasks to streamline onboarding process.}
        \resumeItem{Performed customer requirement analysis and proposed cloud-integrated CRM solutions.}
        \resumeItem{Collaborated with clients in meetings to capture technical and business requirements.}
        \resumeItem{Successfully closed a CRM software deal by identifying client pain points and tailoring solutions.}
        \resumeItem{Delivered actionable insights through data analysis to improve CRM adoption strategy.}
      \resumeItemListEnd  
    
    \resumeSubheading
      {CRM Consultant}{} 
      {Dr.Factory, Malaysia}{March 2025 – June 2025}
      \resumeItemListStart
        \resumeItem{Provided end-to-end CRM consultation services to clients across industries.}
        \resumeItem{Managed system configuration and data migration to new CRM platforms, ensuring data integrity.}
        \resumeItem{Worked closely with clients to customize CRM setups for their unique workflows and objectives.}
        \resumeItem{Trained clients and key users on CRM usage to increase system adoption and long-term success.}
      \resumeItemListEnd  
    
    \resumeSubheading
      {Founder \& Project Consultant}{} 
      {K\&E Tech Innovations, Malaysia}{2025 – Present}
      \resumeItemListStart
        \resumeItem{Established a digital solutions company delivering both landing page websites and dynamic web systems.}
        \resumeItem{Developed landing pages using WordPress with tailored SEO configurations via Yoast SEO plugin.}
        \resumeItem{Integrated Google Analytics to track site performance, visitor behavior, and marketing effectiveness.}
        \resumeItem{Architected full-stack web systems using React for frontend and Firebase for backend services and hosting.}
        \resumeItem{Managed freelance teams across multiple projects, overseeing planning, requirement gathering, and delivery.}
        \resumeItem{Actively involved in technical troubleshooting and solution design to ensure project stability and quality.}
      \resumeItemListEnd  
    % copy and paste above resumeSubheading block to add more 
  \resumeSubHeadingListEnd
\vspace{-12pt}

\end{document}
